### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
Unsolveable solution

\subsection*{How to get infinite solutions with t and s?}

>>>>

Generally a new constraint just needs to be a contradiction to another constraint.

\subsection*{How to get infinite solutions with t and s?}
The equation influence by t and s is:

\begin{equation*}
max: s*x_1+t*x_2
\end{equation*}

One way to get an infinite solution could be to generate a endless loop with values for s and t like:
\begin{eqnarray*}
s=s*x_1\label{inf1}\\ 
t=t*x_2 \label{inf2}\\ 
or\\
s=t*x_2\label{inf3}\\ 
t=s*x_1 \label{inf4}\\ 
\end{eqnarray*}

Best idea of the evening:
Do not assume to only use integers!
Another variant is to define:
\begin{eqnarray*}
	s=\frac{1}{x_1}\\
	t=\frac{1}{x_2}\\ 
\end{eqnarray*}
the result for Z now is 2 and there are infinite many possibilities to get to 2.
